A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-26 paper/paper.Rnw
Add code to equalize images, extra column to pred_prob_plot

source(file.path(codedir, "Generate_Model_Images.R"))
@

@@

<<low-contrast-consistency, fig.cap = "\\mt{Model predictions for images with low contrast. While these images do truly contain a variety of shapes, the diffuse probabilities assigned by the model across all categories indicate that features are obscured by low contrast, which propogates through model training and prediction.}", fig.pos = "p!", out.width = "100%", cache = T>>=
lowcontrast <- list.files(file.path(wd, "images", "consistency", "low-contrast2"), full.names = T)
pred_prob_plot(lowcontrast, loaded_model, sort = F, eer = eers)
@

>>>>

source(file.path(codedir, "Generate_Model_Images.R"))
source(file.path(codedir, "equalize.R"))
@

@@

<<low-contrast-consistency, fig.cap = "Model predictions for images with low contrast. While these images contain a variety of shapes \\svp{(as shown in the color-corrected column on the right)}, the diffuse probabilities assigned by the model across all categories indicate that features are obscured by low contrast, which propogates through model training and prediction.", fig.pos = "p!", out.width = "100%", fig.width = 10/1.2, fig.height = 9/1.2, cache = T>>=
lowcontrast <- list.files(file.path(wd, "images", "consistency", "low-contrast2"), full.names = T)

pred_prob_plot(lowcontrast, loaded_model, sort = F, eer = eers,
               img_path2 = lowcontrast) +
  theme(legend.position = "bottom")
@
